---
title: "Discrete Probability Exercise"
author: "Robert M. Bell"
output: pdf_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Web Analytics
## Q1
```{r hist,  echo=FALSE}
barplot(c(.03,.09,.24,.27,.25,.09,.03),names.arg=c(0,1,2,3,4,5,6),xlab="Visits per Hour")
```

Part 1:

For a given hour the probability that the number of visits will be between 4 and 6 is 10%.

\hfill\break
Part 2:
```{r calls}
calls = c(0,1,2,3,4,5,6)
mean(calls)
var(calls)
sd(calls)
```
Of the number of visits per hour the mean is 3, the variance is 4.66, the standard deviation is 2.16

## Q2

\hfill\break
Part 1:

-Assumptions that should be satisfied for X to obey a binomial distribution B(n,p) are:

n must be the number of trials
  
must have two complementary outcomes

a fixed probability of successe
  
independent trials

\hfill\break
Part 2:

-What is n and what is p in this case:
  
the n is the number of trials 
  
the p is the probablity of success

\hfill\break
Part 3:
```{r student}
dbinom(7, size=11, prob=0.68) 
```
The probability that exactly 7 of the 11 visitors are college students is 23.3%

\hfill\break
Part 4:
```{r expected}
.68 * 11 
```
The expected number of visitors (of the 11) who are college students is 7.5

\hfill\break
Part 5:
```{r sd_expected}
sd(c(1,7))
```
The standard deviation of the number of visitors who are college students is 4.24

\hfill\break

## Q3
Part 1:
```{r mobile_customers}
dbinom(8, size=20, prob=0.38) 
```
The probability that 8 of the 20 randomly chosen consumers will be mobile consumers is 18%

\break
Part 2:
```{r desktop_customers}
sum(dbinom(12:14, size=20, prob=.62))
```
The probability that between 12 and 14 of the 20 randomly chosen consumers will be desktop consumers is 50%

\hfill\break
Part 3:
```{r less_customers}
dbinom(0, size=20, prob=.62)+
dbinom(1, size=20, prob=.62)+
dbinom(2, size=20, prob=.62)+
dbinom(3, size=20, prob=.62)
```
The probability that 3 or fewer of the randomly chosen consumers will be desktop consumers is 0%
\hfill\break

## A Game of Chance
## Q4

\hfill\break
Part 1:
```{r a_answer}
1 / 4
```
The probability that your friend says the answer is “a” is 25%

\hfill\break
Part 2:
```{r b_answer}
1 / 4
```
The probability that your friend says the answer is “b” is 25%

\hfill\break
Part 3:

Since the phoned friend has an 80% probability of picking the correct answer between A and B the stragety should be to go with the friends answer if they select A or B.  If they don't select A or B I should go with answer A because the expected value is still higher than the no answer option.  I would expect to win the full $1,000,000 with the given probabilities between the phone freind and my own guess.  

\break

## Health Care Analytics

## Q5

\hfill\break
Part 1:
The probability that the test will identify the person as having the disease is 94% 

\hfill\break
Part 2:
```{r wrong}
dbinom(1, size=3, prob=.09)
```
The probability that at least one of the three individuals will be identified by your classifier as having the disease is 22%

\hfill\break
Part 3:
```{r has_disease}
round(((.17)*(.91)) / ((.17)*(.91)) + ((.83)*(.08)))
```
If a random person from this area is tested and the results indicate that the person has the disease, the chance that the person actually has the disease is 100%
\hfill\break

## Airline Analytics
## Q6

\hfill\break
Part 1:
```{r show_up}
dbinom(0, size=11, prob=1-.20)+
dbinom(1, size=11, prob=1-.20)+
dbinom(2, size=11, prob=1-.20)+
dbinom(3, size=11, prob=1-.20)+
dbinom(4, size=11, prob=1-.20)+
dbinom(5, size=11, prob=1-.20)  
```
The probability that at most 5 of the 11 persons who purchased first class tickets show up for the flight is 1.1%

\hfill\break
Part 2:
```{r show_up2}
dbinom(10, size=11, prob=1-.20)
```
The probability that exactly 10 of the persons who purchased first class tickets show up for the flight is 24%

\hfill\break
Part 3:
```{r show_up3}
dbinom(11, size=11, prob=1-.20) * 9000
```
The expected profit from 11 first class passengers is $773 

\hfill\break
Part 4:
```{r show_up4}
dbinom(10, size=11, prob=1-.20) * 12000
```
The expected profit from 10 first class passengers is $2834

\hfill\break
Part 5:

The fact that people often travel in groups does affect the independence assumption about passenger behavior.  If the the occourance of B has and an infulence on the outcome of A then the trial will no longer be independent.  So if someone in the travel group affects the outcome of the other traveler the trial is no longer independent. 





